Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2023-02-14 manuscript.Rmd
Update manuscript.Rmd

<!--introduce confirmatory vs. exploratory-->
The scientific community has long pondered the vital distinction between exploration and confirmation, discovery and justification, hypothesis-generating and hypothesis-testing, or prediction and postdiction [@hoyningen-hueneContextDiscoveryContext2006; @shmueliExplainPredict2010, @nosekPreregistrationRevolution2018].
There is a broad consensus that both approaches are necessary for science to progress; exploration for making new discoveries and confirmation for exposing these discoveries to potential falsification and assess in how far it has been corroborated.
Mistaking exploratory findings for empirically confirmed results inflates the the likelihood of believing that there is evidence for a given explanation even if it is false.
A variety of practices, such as researchers' degrees of freedom together with researchers' hindsight bias or naive p-hacking have led to such mistakes becoming commonplace yet unnoticed for a long time.
Recognizing them has led to a crisis of confidence in the empirical sciences [@ioannidisWhyMostPublished2005], and psychology in particular [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
As a response to the crisis, more and more researchers preregister their data collection and analysis plans in advance of the study [@nosekPreregistrationRevolution2018].
They do so to stress the predictive nature of their registered statistical analyses and often with the hopes of obtaining a label that marks the study as "confirmatory".
Indeed, rigorous application of preregistration prevents researchers from reporting a set of results produced by an arduous process of trial and error as a simple confirmatory story [@wagenmakersAgendaPurelyConfirmatory2012] while keeping low false-positive rates.
This promise of a clear distinction between confirmation and exploration has obvious appeal to many who already accepted the practice.
Still, the majority of empirical researchers do not routinely preregister their studies.
One reason may be that some do not find that the theoretical advantages outweigh the practical hurdles, such as specifying every aspect of a theory in advance.
We believe that we can reach a greater acceptance of preregistration by explicating a more general objective of preregistration that benefits all kinds of studies, even those that allow data-dependent decisions.

>>>>

<!--introduce confirmatory vs. exploratory-->
The scientific community has long pondered the vital distinction between exploration and confirmation, discovery and justification, hypothesis-generating and hypothesis-testing, or prediction and postdiction [@hoyningen-hueneContextDiscoveryContext2006; @shmueliExplainPredict2010, @nosekPreregistrationRevolution2018].
There is a broad consensus that both approaches are necessary for science to progress; exploration for making new discoveries and confirmation for exposing these discoveries to potential falsification and assess in how far it has been corroborated.
Mistaking exploratory findings for empirically confirmed results inflates the the likelihood of believing that there is evidence for a given explanation even if it is false.
A variety of practices, such as researchers' degrees of freedom together with researchers' hindsight bias or naive p-hacking have led to such mistakes becoming commonplace yet unnoticed for a long time.
Recognizing them has led to a crisis of confidence in the empirical sciences [@ioannidisWhyMostPublished2005], and psychology in particular [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
As a response to the crisis, more and more researchers preregister their data collection and analysis plans in advance of the study [@nosekPreregistrationRevolution2018].
They do so to stress the predictive nature of their registered statistical analyses; often with the hopes of obtaining a label that marks the study as "confirmatory".
Indeed, rigorous application of preregistration prevents researchers from reporting a set of results produced by an arduous process of trial and error as a simple confirmatory story [@wagenmakersAgendaPurelyConfirmatory2012] while keeping low false-positive rates.
This promise of a clear distinction between confirmation and exploration has obvious appeal to many who already accepted the practice.
Still, the majority of empirical researchers do not routinely preregister their studies.
One reason may be that some do not find that the theoretical advantages outweigh the practical hurdles, such as specifying every aspect of a theory in advance.
We believe that we can reach a greater acceptance of preregistration by explicating a more general objective of preregistration that benefits all kinds of studies, even those that allow data-dependent decisions.
